---
title: "Statistical inference courese project 1"
output: pdf_document
---

## Problem explanation 

The exponential distribution can be simulated in R with rexp(n, lambda) where lambda is the rate parameter. The mean of exponential distribution is 1/lambda and the standard deviation is also also 1/lambda. Set lambda = 0.2 for all of the simulations. In this simulation, you will investigate the distribution of averages of 40 exponential(0.2)s. Note that you will need to do a thousand or so simulated averages of 40 exponentials.

## Simulation 1000 times for 40 exponentials

```{r}
lambda = 0.2
n = 40
nsims = 1:1000
set.seed(1000)
means <- data.frame(x = sapply(nsims, function(x) {mean(rexp(n, lambda))}))
head(means)
```

1. Show where the distribution is centered at and compare it to the theoretical center of the distribution.
```{r}
mean(means$x)

sd(means$x)
```
- Mean of my simulation is `r mean(means$x)` and Expected mean is `r 1/0.2`.

- SD of my simulation is `r sd(means$x)` and Expected SD is `r (1/lambda)/sqrt(n)`.

2. Show how variable it is and compare it to the theoretical variance of the distribution.

```{r}
var(means$x)
```

- Variance of my simulaton is `r var(means$x)` and theoretical variance of the distribution is `r ((1/lambda)/sqrt(40))^2`.

3. Show that the distribution is approximately normal.

```{r}
library(ggplot2)
ggplot(data = means, aes(x = x)) + 
    geom_histogram(aes(y=..density..), fill = I('blue'), 
                   binwidth = 0.20, color = I('black')) +
    stat_function(fun = dnorm, arg = list(mean = 5, sd = sd(means$x)))
```

4. Evaluate the coverage of the confidence interval for 1/lambda: X±1.96S/sqrt(n).

```{r}
mean(means$x) + c(-1,1)*1.96*sd(means$x)/sqrt(nrow(means))
```

**As above simulations, we know that 
the exponential distribution can be simulated and the mean of exponential distribution is 1/lambda and the standard deviation is also also 1/lambda.**


